---
title: "vembedr"
author: "Ian Lyttle"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This package makes it a little easier for you to embed videos from YouTube and Vimeo into your Rmarkdown documents and your Shiny apps.

## Use

```{r}
library("htmltools")
library("vembedr")
```

```{r}
div(align = "center", embed_vimeo("45196609"))
div(align = "center", embed_youtube("dQw4w9WgXcQ"))
```

Due to the unique appeal of this particular video, it behooves me to include some functions to make their inclusion in your work that much easier. Here's some *syntactic* sugar for your synthetic sugar, functions to make it easier for you to get the feel for the different embedding options:

```{r eval=FALSE}
rickroll_vimeo()
rickroll_youtube()
```

These functions just pass their arguments on to `embed_vimeo()` or `embed_youtube()`.

## Installation

At some point, I hope to submit this to CRAN. In the meantime, you can install this package using Github.

```{r eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("ijlyttle/vembedr")
```
