---
title: "vembedr"
author: "Ian Lyttle"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R package makes it a little bit easier for you to embed videos from YouTube and Vimeo into your Rmarkdown documents and your Shiny apps.

This is done by providing functions to generate the HTML embedding-code for each of these services. 

[Github repository](https://github.com/ijlyttle/vembedr)

## Use

```{r}
library("htmltools")
library("vembedr")
```

```{r}
div(align = "center", embed_vimeo("45196609"))
div(align = "center", embed_youtube("dQw4w9WgXcQ", query = list(t = "1m30s")))
```

The unique appeal of this particular video demands some functions to make their inclusion in your work that much easier. So here's some *syntactic* sugar for your synthetic sugar:

```{r eval=FALSE}
rickroll_vimeo()
rickroll_youtube()
```

These functions may make it easier for you to get the feel for the different embedding options, as they just pass their arguments on to `embed_vimeo()` or `embed_youtube()`.

## What it does

These functions simply use the html constructors from the htmltools package.

```{r}
str(rickroll_youtube())
```

Although the class is `shiny.tag`, this does not imply that you need to use Shiny. 

```{r}
print(rickroll_youtube())
```

As you can see, this will output standard HTML code.

## Installation

At some point, I hope to submit this to CRAN. In the meantime, you can install this package using Github.

```{r eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("ijlyttle/vembedr")
```
